On change of priors in one-vs-one classification methods

### 2025-05-08 theory.tex
Fix symmetry definition

\begin{prop}[Fundamental theorem of one-vs-one classification]
	 \label{prop:binary2multi}
	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
\end{prop}
\begin{proof}
	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denote the odds of $C_i$ to $C_j$:
	\begin{align}
		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j}
	\end{align}

@@

\emph{Symmetry} refers to the action of the permutation group which acts both on the classes as well as on multi-class predictions. The action of a permutation $\sigma$ extends to the action on the pairwise matrix $\boldsymbol{R} = (r_{ij})$ by 
\begin{equation}
	 r^\sigma_{i,j} \stackrel{def}{=}  r_{\sigma(i), \sigma(j)}.
\end{equation}
We say that a coupling method $V$ is \emph{symmetric} if 
\begin{align}
		\boldsymbol{v}(\boldsymbol{R})^\sigma = \boldsymbol{v}(\boldsymbol{R}^\sigma)\quad\textrm{for any permutation $\sigma$}.
\end{align}

>>>>

\begin{prop}[Fundamental theorem of one-vs-one classification]
	 \label{prop:binary2multi}
	 Knowledge of binary Bayes classifiers $p_{ij}^\Pi$ determines the multiclass Bayes classifier $\boldsymbol{p}^\Pi$.
\end{prop}
\begin{proof}
	Given a multiclass distribution $\boldsymbol{p} = (p_1, \ldots,p_K)$ on $K$ classes, let $\alpha_{ij}(\boldsymbol{p})$ denote the odds of $C_i$ to $C_j$:
	\begin{align}
		\alpha_{ij}(\boldsymbol{p}) = \frac{p_i}{p_j} \label{eq:alpha}
	\end{align}

@@

\emph{Symmetry} We can define two natural actions on permutation group on $K$-elements. Suppose $\sigma$ is a permutation on $K$ elements.

\begin{itemize}
	\item Given  distributions on the classes $\boldsymbol{p}= (p_1, \ldots, p_K)$, we can define
	\begin{align}
		\sigma(\boldsymbol{p})= (p_{\sigma(1)},p_{\sigma(2)}, \ldots, p_{\sigma(K)}).
	\end{align}
	 \item $\sigma$ also acts on the matrix of binary predictions. Namely, the entry of $\sigma(\boldsymbol{R})$ in $i$-th row and $j$-th column is defined to be $r_{\sigma(i), \sigma(j)}$.
	 \end{itemize}
We say that a coupling method $V$ is \emph{symmetric} if 
\begin{align}
		\sigma(\boldsymbol{v}(\boldsymbol{R})) = \boldsymbol{v}(\sigma(\boldsymbol{R}))\quad\textrm{for any permutation $\sigma$}.
\end{align}
